### 2021-04-15 Paper/Main.tex
just pushing b/c we have done alot

\section{Data}
\label{Data}
The data used for this paper was soured three databases. The daily performance of the individual stock prices was collected from CRSP's primarily daily stock prices. Data on the ESG portfolio and well as the petroleum portfolio was extracted from compustat as the daily average returns for MSCI World ESG Focus Index and S/&P petroleum index. Finally, daily Fama French factors for SMB, CMA,HML, and RMW were sourced from the Kenneth R. French - Data Library.  An ESG factor, demoted as EMP (ESG minus petroleum), was created by taking the  MSCI World ESG Focus Index returns and subtracting them from the  S\&P petroleum index. Petroleum companies act as a stand in for the opposite of ESG as the  petroleum space is particularly inept to adapt to ESG  changes, a fact well documented in academic literature \cite{Frynas2005TheFD}. In addition, in section \ref{Robustness} for robustness I will repeat the analysis replacing the  S\&P petroleum index with S\&P Metals & Mining Select Industry Index as the opposed portfolio for the EMP factor. It has been also well documented that the mining industry also struggles to adapt to ESG factors due to the nature of the industry \cite{Kapelus2002MiningCS}.

 Data was collected between June 2011 and March 2021. The started was determined by the initiation of the MSCI ESG index. With the selected window, CRSP data for daily returns was collected on each available company. Daily returns for the individual companies as well as each of the Fama factors and the EMP factor was collapsed by month by suming the daily changes in each given month and year. The collapses resulted in 830,889 observation for 12,194 unique stocks which gives an average of 68 months of data for each unique security.  Outlined in table are  some of the summary statistics for the raw data.

@@

\section{Methodology}
\label{Methodology}
As discussed in the literature review there are numerous different models for assessing asset pricing and abnormal returns. In this paper I will be using an extension on on Fama French's 2015 paper ``A five factor asset pricing model". This method of analysis is builds off of the famma french three factor model and relies on the 2 pass sort to assign a series of beta decile and size decile based portfolios. Breaking the portfolios into these distinct groups allows for further analysis of the effect across these two factors do asses the abnormal returns.

To determine the beta deciles for individual securities first a beta must be calculate for each security. To calculate the betas, a  simple regression outlined in equation \eqref{prerank_reg} was preformed. In this regression, a vector of  excess market returns in the current period and a vector of market returns from the previous period is regressed on a vector of current periods individual stock excess returns (i.e $R_{i,t}-R_{rf,t}$). The time movements for the data moved in month increments and the length of the vector ranged for 12 month to 60 months depending on the availability of data. Next, the beta values are summed together to get the pre-ranking beta value.

\begin{equation}
    R_{i,t}^e = a_{i,t} + \beta_{i1,t}(R_{m,t}-R_{rf,t})+\beta_{i2,t}(R_{m,t-1}-R_{rf,t-1})+\epsilon_{i,t}
    \label{prerank_reg}
\end{equation}
\begin{equation}
    \beta_{sum} = \sum_{k=1}^2\beta_{ik,t}
\end{equation}

Before assigning the deciles a data cleaning process was applied. A small portion of prerankning beta's are far larger than would be expected, as such these vales were removed from the sample by removing top and bottom 4\% of companies by preranking beta. A similar data cleaning process was also conducted in the Fama french five factor model. In addition to removing the very large and very small preranking beta values I also removed the companies with market capitalization less than 10M dollars in market capitalization. After sorting by the beta decile's size deciles were asigned based on the CRSP NYSE/NYSE American/NASDAQ market capitalization.

*dicuss how we collapse the prolfio from 10 to 2 size

Decile-sorted indexes based on
market capitalization
TO find the beta deciles

To capture abnormal returns we will consider 5 factors that is the 5 factors from the famma french paper small minus big(SMB),CMA, HML, and market portfolio(I.e model, consisting of market, size, value, profitability, and investment factors;). In addition I will ad another term to address how stocks move with the movement to a ESG porlfio. For this purpose we will use the MSCI ESG all world index.

\begin{equation}
\begin{split}
    R_{it}^e = a_i+b_i(R_{Mt}-R_{fr})+s_iSMB_t+ & h_iHML_t+ & r_iRMW_t+c_iCMA_t+e_iEMP_t
    \end{split}
    \label{six_factor_basic_reg}
\end{equation}
In equation \eqref{six_factor_basic_reg} $HML_{t}$ is the difference between the returns on diversified portfolios of high and low book to market stocks, $SMB_{t}$ i the return on a diversified portfolio of small stocks minus the return on a diversified portfolio of big stocks, $RMW_t$ is the difference between the returns on diversified portfolios of stocks with robust and weak profitability,$CMA_{t}$ is the difference between the returns on diversified portfolios of the stocks of low and high investment firms,$EMP_t$ is the difference between MSCI World ESG Focus Index returns and the S\&P petroleum index. finally, $R^e_{it}$ is the return of the individual secutiy minus the risk freee rate ($R_{it}-R_{rf}$)

\section{Results}
\label{Results}

\section{Robustness Checks}
 %as dicussed in section \ref{Data} [talk about using mining instead of petrolum ]
\label{Robustness}

@@

\bibliography{Matt_Bib.bib}{}
\bibliographystyle{plain}
%\nocite{*}
%\printbibliography

\section{Code}
\input{Paper/Code_files}
\end{document}

>>>>

\section{Data}
\label{Data}
The data used for this paper was sourced from three datasets. The daily performance of the individual stock prices was collected from CRSP's primarily daily stock prices. Data on the ESG portfolio and the contra ESG portfolio were extracted from Compustat as the daily average returns for the MSCI World ESG Focus Index and S/&P petroleum index, respectively. Finally, daily Fama French factors for SMB, CMA, HML, and RMW were sourced from the Kenneth R. French - Data Library.  An ESG factor, denoted as EMP (ESG minus petroleum), was created by taking the  MSCI World ESG Focus Index returns and subtracting them from the  S\&P petroleum index. Petroleum companies act as a stand-in for the opposite of ESG as the petroleum space is particularly inept at adapting to ESG  changes, a fact well documented in academic literature \cite{Frynas2005TheFD}. In addition, in section \ref{Robustness} for robustness I will repeat the analysis replacing the  S\&P petroleum index with S\&P Metals & Mining Select Industry Index as the contra ESG portfolio for the EMP factor. It has been also well documented that the mining industry also struggles to adapt to ESG factors due to the nature of the industry \cite{Kapelus2002MiningCS}.

 Data points were collected between June 2011 and March 2021. The started was determined by the initiation of the MSCI ESG index. With the selected window, CRSP data for daily returns were collected on each available company. Daily returns for the individual companies as well as each of the Fama factors and the EMP factor was collapsed by month by summing the daily changes in each given month and year. The collapses resulted in 830,891 observations for 12,194 unique stocks, which gives an average of 68months of data for each unique security—outlined in table 1are some of the summary statistics for the raw data.

@@

\section{Methodology}
\label{Methodology}
As discussed in the literature review there are numerous different models for assessing asset pricing and abnormal returns. In this paper I will be using an extension on on Fama French's 2015 paper ``A five factor asset pricing model". This method of analysis is builds off of the famma french three factor model and relies on the 2 pass sort with an assign series of beta decile and size decile based portfolios. Breaking the portfolios into these distinct groups allows for further analysis of the effect across these two factors to assess relational interdependency.

In the preliminary analysis of the ESG factor I sort securties  on beta as well as size deciles. Each security will be assigned a decile for beta and size according the the CRSP /NYSE american beta decile for beta and the CRSP Nasdaq Market Capitalization portfolio for size. After sorting each of the securities by Beta and size decile  300,264 of the original 830,889 data points had matches for both portfolios. To capture the effect of size and each of the Fama French factors and ESG factor I ran the reguression in equation \eqref{six_factor_basic_reg} on the cleaned data set.

\begin{equation}
\begin{split}
    R_{i,t}^e = a_i+b_i(R_{M,t}-R_{fr,t})+s_iSMB_t+ & h_iHML_t+ & r_iRMW_t+c_iCMA_t+e_iEMP_t
    \end{split}
    \label{six_factor_basic_reg}
\end{equation}
Where:
\begin{center}
    $R_{i,t}^e = R_{it}-R_{rf,t}$
\end{center}

***Dicuss the second pass***

\begin{equation}
    E[R^e_{t}]= b_t\lambda_1+s_t\lambda_2 +h_t \lambda_3 +r_t\lambda_4 +c_t \lambda_4 + e_t \lambda_5
\end{equation}
In equation \eqref{six_factor_basic_reg}

\section{Results}
\label{Results}
table 3 in represents a matrix of values for the first pass in the fama french two pass sort, described in equation \eqref{six_factor_basic_reg}. The column axis is the distinct size deciles where 1 is the smallest market cap companies and 10 is the declie with the largest market cap companies. The row axis includes estimated coefficients for the intercept, five Fama French factors and the EMS factor. $HML_{t}$ is the difference between the returns on diversified portfolios of high and low book to market stocks, $SMB_{t}$ i the return on a diversified portfolio of small stocks minus the return on a diversified portfolio of big stocks, $RMW_t$ is the difference between the returns on diversified portfolios of stocks with robust and weak profitability,$CMA_{t}$ is the difference between the returns on diversified portfolios of the stocks of low and high investment firms,$EMP_t$ is the difference between MSCI World ESG Focus Index returns and the S\&P petroleum index. finally, the intercept is the excess returns for the given decile.The results in this table demonstrate that for HML, CMA and EMP factor there is a size based relationship where in the larger the size decile the smaller the effect is on the factor. In addition, the EMP factor also exhibits a  a consistent negative relationship between the EGS factor and returns. This relationship indicates that investors are actually paying a premium to invest in ESG companies over the contra EGS counterparts.

Moving onto the 
Analysing our results from the methology  stages of the two pass sort we would expect to see

\begin{center}
\input{Paper/prelim_size}\\
\textbf{Table 3:} Size decile by estimated coefficients for the  five fama french factors and EMP factor
\end{center}
\begin{center}
\input{Paper/p_vals_size_prelim}\\
\textbf{Table 4:} Size decile by p-values for table 3

\end{center}

\begin{center}
\input{Paper/prelim_beta}\\
\textbf{Table 5:} beta decile by estimated coefficients for the  five fama french factors and EMP factor
\end{center}

To capture abnormal returns we will consider 5 factors that is the 5 factors from the famma french paper small minus big(SMB),CMA, HML, and market portfolio(I.e model, consisting of market, size, value, profitability, and investment factors;). In addition I will ad another term to address how stocks move with the movement to a ESG porlfio. For this purpose we will use the MSCI ESG all world index. 
\section{Robustness Checks}
 %as dicussed in section \ref{Data} [talk about using mining instead of petrolum ]
\label{Robustness}

@@

\bibliography{Matt_Bib.bib}{}
\bibliographystyle{plain}

\newgeometry{margin=.15in}
\input{Code/data/size_summary_stat_size}\\

\vspace{1cm}
\textbf{Table 2:}things\\
\vspace{1cm}

\clearpage
\restoregeometry

%\nocite{*}
%\printbibliography

%\section{Code}
%\input{Paper/Code_files}
\end{document}
